MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-03-25 MAESTROeX_I/results.tex
scaling figures

\subsection{Scaling}
In Figure XXX we show weak scaling results for a spherical, full-star sub-chandrasekhar mass white dwarf calculation.
The x-axis represents total core count (in this case, the total number of OpenMP threads), and the y-axis is the wallclock time per time step.
These simulations were performed using the NERSC cori system on the Intel Xeon Phi (KNL) partition.
We split each KNL node to contain 4 MPI processes with 16 threads each.
The computational domain for each simulation is divided into $64^3$ grid cells, and we assign 1 MPI process to each grid.
We used simulations ranging from $256^3$ grid cells (64 MPI processes, corresponding to 1024 total threads) up to $1536^3$ grid cells (13,824 MPI processes, corresponding to 221,184 total threads).
Note that the largest simulation used roughly 36\% of the entire computational system.
We see that the total increas in wallclock time from the smallest to largest simulation is roughly 41\%, which is quite remarkable given that there are 3 linear solves per time step.
\MarginPar{Making new plots splitting out projections vs. everything else.}

>>>>

\subsection{Scaling}
In Figure XXX we show weak scaling results for convection preceding ignition in a spherical, full-star sub-Chandrasekhar mass white dwarf.
These results are representative of simulations used in actual scientific studies; see \cite{MAESTRO_convection,MAESTRO_AMR}.
For this scaling study we use a spatially uniform grid (no AMR).

These simulations were performed using the NERSC cori system on the Intel Xeon Phi (KNL) partition.

We compare the original BoxLib-based MAESTRO implementation to the AMReX MAESTROeX implementation with the classic algorithm (original temporal integrator).

We also include a plot of MAESTROeX without base state evolution.

The y-axis is the wallclock time per time step, and the x-axis represents total core count (in this case, the total number of OpenMP threads).

We split each KNL node to contain 4 MPI processes with 16 threads each.  We note that KNL can support up to 272 hardware threads per node (i.e., 68 hardware threads per MPI process since here we assign 4 MPI processes per node), but testing reveals that using $64^3$ grids, additional threads do not decrease the wallclock time.  Thus, the more accurate measure of weak scaling is to consider the number of MPI processes, since the scaling plot would look virtually identical for larger thread counts.

In principle, we could use larger grids and use more OpenMP threads per MPI process, but the overall wallclock time would increase.

The computational domain for each simulation is divided into $64^3$ grid cells, and we assign 1 MPI process to each grid.
We used simulations ranging from $256^3$ grid cells (64 MPI processes, corresponding to 1024 total threads) up to $1536^3$ grid cells (13,824 MPI processes, corresponding to 221,184 total threads).
Note that the largest simulation used roughly 36\% of the entire computational system.
We see that the total increas in wallclock time from the smallest to largest simulation is roughly 41\%, which is quite remarkable given that there are 3 linear solves per time step.

Include a plot showing the linear solver scaling, and a discussion about how the bottleneck for typical MAESTRO simulations is the averaging operator.

\MarginPar{Making new plots splitting out projections vs. everything else.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=2.75in]{./figs/MAESTRO_scaling1}
\includegraphics[width=2.75in]{./figs/MAESTRO_scaling2}
\caption{\label{fig:scaling} (Left) Weak scaling results for a spherical, full-star sub-Chandrasekhar mass white dwarf calculation using the original MAESTRO code, MAESTROeX, and MAESTROeX with base state evolution disabled.  Shown is the average wallclock time per time step.
(Right) Weak scaling results showing the average wallclock time per time step spent in the cell-centered and nodal linear solvers within a full time step of the aforementioned simulations.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
